---
title: "p8105_hw1_ar4459"
author: "ASHLEY ROMO"
date: "2023-09-21"
output: github_document 
---


# Problem 1
```{r}

library(tidyverse)

library(moderndive)

data("early_january_weather")

```

The following are all the variables in the early_january_weather dataset: origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, percip, pressure, visib, and time_hour. Important variables are temp, time_hour, day, hour because they explain how the temperature changes throughout the day at each time point and hour.

The size of the dataset includes `r nrow(early_january_weather) ` rows and `r ncol(early_january_weather)` columns.

```{r}

mean (pull(early_january_weather, temp))

```

The mean temperature is `r mean(pull(early_january_weather, temp))`.

```{r}

ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()

ggsave("scatter_time_temp.pdf")

```

The pattern seen in the scatter plot is monotonic. The overall pattern is increasing. There is also a notable change in temperature throughout the day.

# Problem 2
```{r}
data_frame = 
  tibble(
    rand_samp = rnorm (10, mean = 0),
    log_vec = rand_samp >- 0,
    char_vec = c("Hello!", "My", "name", "is", "Ashley.", "I", "am", "a", "master", "student"),
    fact_vec = factor(c("low", "low", "high", "moderate", "high", "moderate", "low", "low", "low", "moderate"))
)
```
